ShabbyPages: A Recipe for Repeatable, Synthetic, Modern Document Images

### 2023-02-11 paper/paper.tex
revert table, fix PSNR arrow pointing wrong direction

\begin{table}[]
    \centering
    \caption{Summary of datasets for document denoising and binarization tasks.}
    \label{tab:datasets}
    \begin{tabular}{lcllllllll}
        \textbf{Dataset} &
        \rot{80}{\textbf{Dataset Size}}
            & \rot{80}{\textbf{Synthetic Noise}}
            & \rot{80}{\textbf{Ground-Truths}}
            & \rot{80}{\textbf{Diversity}}
            & \rot{80}{\textbf{Font size}}
            & \rot{80}{\textbf{Paper styles}}
            & \rot{80}{\textbf{Multilingual}}
            & \rot{80}{\textbf{Contains graphics}}
            & \rot{80}{\textbf{Reproducible}}\\
            \midrule
         \emph{ShabbyPages} (ours)~ & 6,202~ & \cmark & \cmark & 0.488~ & multi~ & multi~ & \cmark & \cmark & \cmark \\
         \emph{NoisyOffice} \cite{ref_NoisyOffice} & 72  & \cmark & \cmark & 0.317 & 16pt & 1 & \xmark & \xmark & \xmark \\
         DocCreator \cite{ref_DocCreator} & & \cmark & \xmark & & & & & &\cmark\\
         DDI-100 \cite{ddi-100-2019} & & \cmark & \cmark & & & & & & \xmark\\
         DIBCO-9 \cite{dibco-09} & & & & & & & & & n/a \\
         DIBCO-10 \cite{dibco-10} & 10 & \xmark & \cmark & & multi & multi & \xmark & \xmark & n/a \\
         DIBCO-11 \cite{dibco-11} & 16 & \xmark & \cmark & & multi & multi & \cmark & \xmark & n/a\\
         DIBCO-12 \cite{dibco-12} & 14 & \xmark & \cmark & & multi & multi & \xmark & \xmark & n/a \\
         DIBCO-13 \cite{dibco-13} & 16 & \xmark & \cmark & & multi & multi & \cmark & \xmark & n/a \\
         H-DIBCO-14 \cite{dibco-14} & 10 & \xmark & \cmark & & multi & multi & \cmark & \xmark & n/a \\
         H-DIBCO-16 \cite{dibco-16} & 10 & \xmark & \cmark & & multi & multi & \cmark & \xmark & n/a \\
         DIBCO-17 \cite{dibco-17} & 20 & \xmark & \cmark & & multi & multi & \cmark & \xmark & n/a \\
         H-DIBCO-18 \cite{dibco-18} & 10 & \xmark & \cmark & & multi & multi & \cmark & \xmark & n/a\\
         DIBCO-19 \cite{dibco-19} & & \xmark & & & & & & & n/a\\
         Bickley Diary \cite{bickley-diary} & & & & n/a & & & & & n/a\\
         PHIBD & & & & & & & & & n/a\\
         TQBC & & & & & & & & & n/a\\
         %LS-HDIB \cite{ls-hdib-2021} & & \cmark & & & & & & & \\
         \bottomrule
    \end{tabular}
\end{table}

@@

\begin{table}[]
    \centering
    \caption{Document image binarization performance of a NAFNet model trained and tested on \emph{ShabbyPages} and \emph{NoisyOffice}.}
    \scalebox{0.9}{
    \begin{tabular}{lllll}
    \toprule
    \textbf{Training Set~~} & \textbf{Test Set} & \textbf{SSIM$\uparrow$~} & \textbf{PSNR$\downarrow$~} \textbf{RMSE$\downarrow$~}\\
        \midrule
        \textsf{ShabbyPages} & \textsf{NoisyOffice-real} & \textbf{0.947} & \textbf{38.098} & \textbf{3.205}\\
        \textsf{NoisyOffice-sim} & \textsf{ShabbyPages} & 0.811 & 34.562 & 5.384\\
        \bottomrule
    \end{tabular}}
    \label{tab:binarization_results}
\end{table}

>>>>

\begin{table}[]
    \centering
    \caption{Summary of datasets for document binarization (above line) and document denoising (below line) tasks.}
    \label{tab:datasets}
    \begin{tabular}{lcllllllll}
        \textbf{Dataset} &
        \rot{80}{\textbf{Dataset Size}}
            & \rot{80}{\textbf{Synthetic Noise}}
            & \rot{80}{\textbf{Ground-Truths}}
            & \rot{80}{\textbf{Diversity}}
            & \rot{80}{\textbf{Mult. font sizes}}
            & \rot{80}{\textbf{Mult. paper styles}}
            & \rot{80}{\textbf{Multilingual}}
            & \rot{80}{\textbf{Contains graphics}}
            & \rot{80}{\textbf{Reproducible}}\\
            \midrule
         DIBCO-9 \cite{dibco-09} & 10 & \xmark & \cmark &  & \cmark & \cmark & \cmark & \xmark & n/a \\
         DIBCO-10 \cite{dibco-10} & 10 & \xmark & \cmark & & \cmark & \cmark & \xmark & \xmark & n/a \\
         DIBCO-11 \cite{dibco-11} & 16 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a\\
         DIBCO-12 \cite{dibco-12} & 14 & \xmark & \cmark & & \cmark & \cmark & \xmark & \xmark & n/a \\
         DIBCO-13 \cite{dibco-13} & 16 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a \\
         H-DIBCO-14 \cite{dibco-14} & 10 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a \\
         H-DIBCO-16 \cite{dibco-16} & 10 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a \\
         DIBCO-17 \cite{dibco-17} & 20 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a \\
         H-DIBCO-18 \cite{dibco-18} & 10 & \xmark & \cmark & & \cmark & \cmark & \cmark & \xmark & n/a\\
         %DIBCO-19 \cite{dibco-19} & & \xmark & & & & & & & n/a\\ % SL: I can't find this dataset online
         Bickley Diary \cite{bickley-diary} & 7 & \xmark & \cmark &  & \xmark & \xmark & \xmark & \xmark & n/a\\
         PHIBD \cite{nafchi-2013-icdar} & 15 & \xmark & \cmark &  & \cmark & \cmark & \xmark & \xmark & n/a\\
         %TQBC & & & & & & & & & n/a\\ % SL: I can't find this dataset online
         \midrule
         NoisyOffice \cite{ref_NoisyOffice} & 72  & \cmark & \cmark & 0.317 & \cmark & \xmark & \xmark & \xmark & \xmark \\
         DocCreator \cite{ref_DocCreator} & 6,059 & \cmark & \cmark & & \cmark & \cmark & \cmark & \xmark &\cmark\\
         %LS-HDIB \cite{ls-hdib-2021} & & \cmark & & & & & & & \\
         DDI-100 \cite{ddi-100-2019} & 100k+~ & \cmark & \cmark & & & & & & \xmark\\
         ShabbyPages (ours)~ & 6,202~ & \cmark & \cmark & 0.488~ & \cmark~ & \cmark~ & \cmark & \cmark & \cmark \\
         \bottomrule
    \end{tabular}
\end{table}

@@

\begin{table}[]
    \centering
    \caption{Document image binarization performance of a NAFNet model trained and tested on \emph{ShabbyPages} and \emph{NoisyOffice}.}
    \scalebox{0.9}{
    \begin{tabular}{lllll}
    \toprule
    \textbf{Training Set~~} & \textbf{Test Set} & \textbf{SSIM$\uparrow$~} & \textbf{PSNR$\uparrow$~} \textbf{RMSE$\downarrow$~}\\
        \midrule
        \textsf{ShabbyPages} & \textsf{NoisyOffice-real} & \textbf{0.947} & \textbf{38.098} & \textbf{3.205}\\
        \textsf{NoisyOffice-sim} & \textsf{ShabbyPages} & 0.811 & 34.562 & 5.384\\
        \bottomrule
    \end{tabular}}
    \label{tab:binarization_results}
\end{table}
